\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-05-09 doc/paper.tex
updating speed test results (including non-fv FS variant)

We compare the run-time of the four different spectrum generators
FlexibleSUSY (version 0.5.4), Softsusy (version 3.4.0), SPheno
(3.2.4), SPhenoMSSM (generated with SARAH 4.1.0 and linked against
SPheno 3.2.4).  FlexibleSUSY and Softsusy were compiled with g++ 4.8.0
and Intel ifort 13.1.3 20130607.  SPheno and SPhenoMSSM were compiled
with Intel ifort 13.1.3 20130607\footnote{We are using Intel's ifort
  compiler, instead of gfortran, because it decreases the run-time of
  SPheno and SPhenoMSSM by approximately a factor $1.5$.}.  We're
generating random CMSSM parameter points with $m_0\in [50,1000]$

@@

\tablename~\ref{tab:run-time-comparison}.  The first row shows the

@@

The second row shows the run-time on a Intel Core2 Duo (P8600) where
both cores were enabled.  In the third row a Intel Xeon (L5640) was
used, which has $6$ CPU cores.

@@

    FlexibleSUSY 0.5.4    & $0.151\unit{s}$    & $0.114\unit{s}$   & $0.091\unit{s}$\\
    Softsusy 3.4.0        & $0.174\unit{s}$    & $0.169\unit{s}$   & $0.162\unit{s}$\\
    SPheno 3.2.4          & $0.119\unit{s}$    & $0.115\unit{s}$   & $0.108\unit{s}$\\
    SPhenoMSSM 4.1.0${}^*$ & $0.416\unit{s}$    & $0.401\unit{s}$   & $0.366\unit{s}$\\

@@

  \caption{Average run-time for random CMSSM parameter points.
    FlexibleSUSY and Softsusy were compiled
    with g++ 4.8.0 and ifort 13.1.3 20130607.
    SPheno, SPhenoMSSM were
    compiled with ifort 13.1.3 20130607.
    ${}^*$SPhenoMSSM was generated with SARAH 4.1.0 and linked
    against SPheno 3.2.4.}

@@

We find that on the single-core machine SPheno is fastest with
$0.119\unit{s}$, and FlexibleSUSY is second with $0.151\unit{s}$.  In
the case of 2 or 6 CPU cores, FlexibleSUSY is fastest with
$0.114\unit{s}$ and $0.091\unit{s}$, respectively.  The reason is that
FlexibleSUSY calculates each pole mass in a separate thread, and
therefore benefits from multi-core CPUs.

>>>>

We compare the run-time of five different CMSSM spectrum generators:
\begin{itemize}
\item FlexibleSUSY-FV (version 1.0.0), which is based on SARAH's MSSM
  model file that allows flavour violation,
\item FlexibleSUSY-NoFV (version 1.0.0), without flavour violation
\item Softsusy (version 3.4.0), without flavour violation
\item SPheno (3.2.4), without flavour violation
\item SPhenoMSSM (generated with SARAH 4.1.0 and linked against SPheno
  3.2.4), which uses SARAH's MSSM model file that includes flavour
  violation.
\end{itemize}
FlexibleSUSY and Softsusy were compiled with g++ 4.8.0 and Intel ifort
13.1.3 20130607.  SPheno and SPhenoMSSM were compiled with Intel ifort
13.1.3 20130607\footnote{We are using Intel's ifort compiler, instead
  of gfortran, because it decreases the run-time of SPheno and
  SPhenoMSSM by approximately a factor $1.5$.}.  We're generating
$2\cot 10^{4}$ random CMSSM parameter points with $m_0\in [50,1000]$

@@

\tablename~\ref{tab:run-time-comparison}.  The first column shows the

@@

The second column shows the run-time on a Intel Core2 Duo (P8600)
where both cores were enabled.  In the third column a Intel Xeon
(L5640) was used, which has $6$ CPU cores.

@@

    FlexibleSUSY-NoFV 0.5.4 & $0.086\unit{s}$    & $0.079\unit{s}$   & $0.060\unit{s}$\\
    SPheno 3.2.4            & $0.119\unit{s}$    & $0.114\unit{s}$   & $0.101\unit{s}$\\
    Softsusy 3.4.0          & $0.175\unit{s}$    & $0.171\unit{s}$   & $0.147\unit{s}$\\
    FlexibleSUSY-FV 0.5.4   & $0.150\unit{s}$    & $0.113\unit{s}$   & $0.074\unit{s}$\\
    SPhenoMSSM 4.1.0${}^*$  & $0.415\unit{s}$    & $0.401\unit{s}$   & $0.370\unit{s}$\\

@@

  \caption{Average run-time of CMSSM spectrum generators for
    for random parameter points.  The upper }

@@

Under both the non-flavor violating spectrum generators
FlexibleSUSY-NoFV, Softsusy and SPheno (first three rows) as well as
the flavor violating ones FlexibleSUSY-NoFV and SPhenoMSSM (4th and
5th row) we find that \fs is significantly fastest.  We also find that
increasing the number of CPU cores reduces the run-time of \fs.  The
reason is that \fs calculates each pole mass in a separate thread, and
therefore benefits from multi-core CPUs.  Under the hand-written CMSSM
spectrum generators SPheno and Softsusy we find that SPheno is fastest
on average.
